---
title: "Introduction to ANOVABNPTestR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to ANOVABNPTestR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo = FALSE}
library(ggplot2)
library(ANOVABNPTestR)
```


```{r printed-setup, eval = FALSE}
library(ggplot2)
library(ANOVABNPTestR) 
# remember: you need to ANOVABNPTestR::setup() at least one time
```

To explore the basic capabilities of `ANOVABNPTestR`, we'll use the dataset 
`example_01`. This is a simulated sample with 1.000 registers, a continuous
response (`y`) and 2 factors (`x1` and `x2`), where the combination
`x1 = x2 = 1` is the *reference group*.

First, let us plot a boxplot of `y` for each combination of `x1` and `x2`:

```{r}
ggplot(ANOVABNPTestR::example_01, aes(y = y)) + 
  geom_boxplot() +
  facet_wrap(
    nrow = 1,
    vars(x1, x2), 
    labeller = "label_both"
  ) +
  theme_classic() + 
  theme(panel.spacing = unit(1, "lines"))
```

This plot suggests weak simple effects (relative to the reference group), but a 
strong interaction effect. However, without a formal test, we cannot be sure. 

ANOVABNPTestR aims to provide tools for testing the existence of simple and 
interaction effects, using a flexible Bayesian model.

<!-- ### Fitting the model -->

<!-- First, we need to train the model. As our response takes values on the real  -->
<!-- line, we should use `anova_bnp_normal()` (see `anova_bnp_poisson()` for  -->
<!-- counts and `anova_bnp_bernoulli()` for Boolean variables): -->
<!-- ```{r, message = FALSE} -->
<!-- yvec <- example_01[[1]] -->
<!-- Xmat <- example_01[, 2:3] |> as.matrix() -->
<!-- fit <- anova_bnp_normal(yvec, Xmat) -->
<!-- ``` -->

<!-- ### Testing for simple effects -->

<!-- Once the model is trained, we can test for simple effects using  -->
<!-- `hypothesis_post_simple()`: -->
<!-- ```{r} -->
<!-- hypothesis_post_simple(fit) -->
<!-- ``` -->
<!-- In this tibble, `var1` specifies the factor into consideration, and `prob`  -->
<!-- is the posterior probability of having a simple effect for that factor. As  -->
<!-- `prob` is always low, there is little support for simple effects. -->

<!-- ### Testing for interaction effects -->

<!-- In a similar, we can test for interaction effects using  -->
<!-- `hypothesis_post_interaction()`: -->
<!-- ```{r} -->
<!-- hypothesis_post_interaction(fit) -->
<!-- ``` -->
<!-- In this tibble, `var1` and `var2` specify the interaction into consideration,  -->
<!-- and `prob` is the posterior probability of having a simple effect for that -->
<!-- interaction. As `prob` nearly 1, there is a great support for an  -->
<!-- interaction effect. -->

<!-- ### Plotting simple effects -->

<!-- In addition to the main tests functions, ANOVABNPTestR can also plot the  -->
<!-- posterior predictive density (ppd) of the response under some common scenarios.  -->
<!-- For example, the function `predictive_plot_simple()` displays the ppd for each  -->
<!-- level of a particular factor, while setting the other factors at their  -->
<!-- reference level. -->

<!-- ```{r, message = FALSE} -->
<!-- predictive_plot_simple(fit, 1) + -->
<!--   theme_classic() -->
<!-- ``` -->

<!-- As you can see, there is nearly no difference between the group distributions,  -->
<!-- in agreement with the output of our tests. -->

<!-- ### Plotting interaction effects -->

<!-- In a similar way, the function `predictive_plot_interaction()` displays the ppd  -->
<!-- for each level of a particular interaction, while setting the other factors at  -->
<!-- their reference level. -->

<!-- ```{r, message = FALSE} -->
<!-- predictive_plot_interaction(fit, 1, 2) + -->
<!--   theme_classic() -->
<!-- ``` -->

<!-- As you can see, there is marked difference between the group distributions,  -->
<!-- again in agreement with the output of our tests. -->
