---
title: "Introduction to ANOVABNPTestR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to ANOVABNPTestR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
  
```{r, include = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
comment = "#>"
)
```

```{r setup, echo = FALSE}
library(ggplot2)
library(ANOVABNPTestR)
```


```{r printed-setup, eval = FALSE}
library(ggplot2)
library(ANOVABNPTestR) 
# Remember: you must call ANOVABNPTestR::setup() at least one time
```

To explore the basic capabilities of `ANOVABNPTestR`, we'll use the simulated
dataset `example_01`. This dataset contains 1.000 registers, a continuous 
response (`y`) and 2 factors (`x1` and `x2`), with `x1 == x2 == 1` 
representing the *control group*.

First, let us plot a boxplot of `y` for each combination of `x1` and `x2`:

```{r}
data <- ANOVABNPTestR::example_01
data |>
  ggplot2::ggplot(ggplot2::aes(y = y)) + 
  ggplot2::geom_boxplot() +
  ggplot2::facet_wrap(
    nrow = 1,
    ggplot2::vars(x1, x2), 
    labeller = "label_both"
  ) +
  ggplot2::theme_classic(base_size = 15) + 
  ggplot2::theme(
    panel.spacing = ggplot2::unit(1, "lines"),
    axis.title.x = ggplot2::element_blank(),
    axis.ticks.x = ggplot2::element_blank(),
    axis.text.x = ggplot2::element_blank()
  )
```

This plot suggests that the only different cell is the one with `x1 == x2 == 2`.
However, without a formal test, we cannot be sure. `ANOVABNPTestR` solves this
issue using a BNP model.

### Fitting the model

First, we must fit the model. As our responses take values on the real
line, we can use `anova_bnp_normal()` (see `anova_bnp_berpoi()` for
counts and `anova_bnp_bernoulli()` for Boolean variables):

```{r, message = FALSE, eval = FALSE}
yvec <- example_01[[c("y")]]
Xmat <- example_01[, c("x1", "x2")] |> as.matrix()
my_fit <- ANOVABNPTestR::anova_bnp_normal(yvec, Xmat)
```














<!-- ### Testing for simple effects -->

<!-- Once the model is trained, we can test for simple effects using -->
<!-- `hypothesis_post_simple()`: -->
<!--   ```{r, eval = FALSE} -->
<!-- hypothesis_post_simple(fit) -->
<!-- ``` -->
<!-- In this tibble, `var1` specifies the factor into consideration, and `prob` -->
<!-- is the posterior probability of having a simple effect for that factor. As -->
<!-- `prob` is always low, there is little support for simple effects. -->

<!-- ### Testing for interaction effects -->

<!-- In a similar, we can test for interaction effects using -->
<!-- `hypothesis_post_interaction()`: -->
<!--   ```{r, eval = FALSE} -->
<!-- hypothesis_post_interaction(fit) -->
<!-- ``` -->
<!-- In this tibble, `var1` and `var2` specify the interaction into consideration, -->
<!-- and `prob` is the posterior probability of having a simple effect for that -->
<!-- interaction. As `prob` nearly 1, there is a great support for an -->
<!-- interaction effect. -->

<!-- ### Plotting simple effects -->

<!-- In addition to the main tests functions, ANOVABNPTestR can also plot the -->
<!-- posterior predictive density (ppd) of the response under some common scenarios. -->
<!-- For example, the function `predictive_plot_simple()` displays the ppd for each -->
<!-- level of a particular factor, while setting the other factors at their -->
<!-- reference level. -->

<!-- ```{r, message = FALSE, eval = FALSE} -->
<!-- predictive_plot_simple(fit, 1) + -->
<!--   theme_classic() -->
<!-- ``` -->

<!-- As you can see, there is nearly no difference between the group distributions, -->
<!-- in agreement with the output of our tests. -->

<!-- ### Plotting interaction effects -->

<!-- In a similar way, the function `predictive_plot_interaction()` displays the ppd -->
<!-- for each level of a particular interaction, while setting the other factors at -->
<!-- their reference level. -->

<!-- ```{r, message = FALSE, eval = FALSE} -->
<!-- predictive_plot_interaction(fit, 1, 2) + -->
<!--   theme_classic() -->
<!-- ``` -->

<!-- As you can see, there is marked difference between the group distributions, -->
<!-- again in agreement with the output of our tests. -->
